\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-17 evaluation.tex
fixes

Environmental modeling is a core activity of using \psharp. It is required for \emph{closing the environment} of a system under test and making it amenable to systematic testing. Table~\ref{tab:stats} presents program statistics for our three case studies. We report: lines of code for the system under test (\#LoC); number of bugs found in the system (\#B); lines of \psharp code for the environmental model (\#LoC); number of machines (\#M); number of state transitions (\#ST); and number of action handlers (\#AH).

>>>>

Environmental modeling is a core activity of using \psharp. It is required for \emph{closing the environment} of a system-under-test and making it amenable to systematic testing. Table~\ref{tab:stats} presents program statistics for our three case studies. We report: lines of code for the system-under-test (\#LoC); number of bugs found in the system (\#B); lines of \psharp code for the environmental model (\#LoC); number of machines (\#M); number of state transitions (\#ST); and number of action handlers (\#AH).

### 2015-09-17 related.tex
fixes

\psharp is most closely related to \textsc{MoDist}~\cite{yang2009modist}, a model checker that can be applied on unmodified distributed systems. To achieve this, the tool uses binary instrumentation (reuses the instrumentation engine of the D$^3$S testing tool) to expose all actions of the system under test, and then uses a model checking engine to systematically explore these actions. \textsc{MoDist} also provides a virtual clock manager that can simulate timeouts and accelerate the passage of time. A major limitation of \textsc{MoDist} is that it must be applied on a whole system, which does not scale for production systems. In contrast, \psharp has built-in support for modeling the environment of individual components of a system, which allows the tool to achieve scalability. Further, \psharp is an extension of the \csharp language and has built-in systematic testing support; it does not need to perform binary instrumentation which can be computationally expensive.

>>>>

\psharp is most closely related to \textsc{MoDist}~\cite{yang2009modist}, a model checker that can be applied on unmodified distributed systems. To achieve this, the tool uses binary instrumentation (reuses the instrumentation engine of the D$^3$S testing tool) to expose all actions of the system-under-test, and then uses a model checking engine to systematically explore these actions. \textsc{MoDist} also provides a virtual clock manager that can simulate timeouts and accelerate the passage of time. A major limitation of \textsc{MoDist} is that it must be applied on a whole system, which does not scale for production systems. In contrast, \psharp has built-in support for modeling the environment of individual components of a system, which allows the tool to achieve scalability. Further, \psharp is an extension of the \csharp language and has built-in systematic testing support; it does not need to perform binary instrumentation which can be computationally expensive.
